---
title: "STAT 542 Final Project"
author: "Elisa Chen"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rmgarch)
library(rugarch)
```

## TODO:
1) Fit the BIS data as exogenous variables. 
2) Calculate the RMSE for all the data
3) Tune hyperparameters --> look at the pacf plots to determine which ones. 
3) Fit for rolling forecasts!


```{r read in data, echo = FALSE}
rris_diff <- read.csv(
  "/Users/edawg/Desktop/Duke/Time Series/Heart-Rate-Variability-Repo/02_code/rris_diff.csv"
)

rris <- read.csv("/Users/edawg/Desktop/Duke/Time Series/Heart-Rate-Variability-Repo/02_code/rris.csv")
```

```{r}
rris_diff
```


# Loading GARCH Model

```{r}
#model setup of GARCH(1,1)
uspec <- multispec(replicate(28, ugarchspec(mean.model = list(armaOrder = c(4, 3)))))

#fit all 28 patients
#multf <- multifit(uspec, rris_diff)

#VAR fit
varFit <- varxfit(rris_diff, p = 20, constant=TRUE, exogen = NULL)

#forecasts for each patient
forecasts <- varxforecast(rris_diff, varFit$Bcoef, p = 20, out.sample = 400, n.ahead = 400, n.roll = 0, mregfor = NULL)
```


#Plot predictions for a single patient
```{r}
# plot for a single patient
patient_num = 2
plot(time, rris_diff[, patient_num], type = 'l')
    lines(x = seq(from = start + 1/4, to = 960, by = 1/4) , y = forecasts[, patient_num, 1], type = 'l', col = 'red')
```

#Plot for all patients

```{r}
par(mar = c(1, 1, 3, 1))
par(mfrow=c(4,7))

time <- seq(from = 1/4, to = 960, by = 1/4)
patient_num= 1
sample_num = 400
start = 960 - (sample_num / 4)

for (k in 1:4) {
  for (l in 1:7) {
    #signal <- cos(2 * pi * 5 * time) + A * cos(2 * pi * 10 * time + alpha)
    #plot(time, signal, type='l', xlab = "", ylab = "")
    plot(time, rris_diff[, patient_num], type = 'l')
    lines(x = seq(from = start + 1/4, to = 960, by = 1/4) , y = forecasts[, patient_num, 1], type = 'l', col = 'red')
    patient_num = patient_num + 1
  }
}
```








## EDA

Every subject's data is the same. At 6 minutes, that's where they get cut. We want to see what's the impact before and after. 

```{r}
BIS_1 <- read.csv('https://raw.githubusercontent.com/celisa/Heart-Rate-Variability-Repo/main/01_data/06233283.ECG2442913AnesEvents-6%2B10mins_BIS.txt')

RRI_1 <- read.csv('https://raw.githubusercontent.com/celisa/Heart-Rate-Variability-Repo/main/01_data/06233283.ECG2442913AnesEvents-6%2B10mins_RRI.txt')

BIS_2 <- read.csv('https://raw.githubusercontent.com/celisa/Heart-Rate-Variability-Repo/main/01_data/3578243.ECG2177606AnesEvents-6%2B10mins_BIS.txt')

RRI_2 <- read.csv('https://raw.githubusercontent.com/celisa/Heart-Rate-Variability-Repo/main/01_data/3578243.ECG2177606AnesEvents-6%2B10mins_RRI.txt')

BIS_3 <- read.csv('https://raw.githubusercontent.com/celisa/Heart-Rate-Variability-Repo/main/01_data/7195417.ECG3710114AnesEvents-6%2B10mins_BIS.txt')

RRI_3 <- read.csv('https://raw.githubusercontent.com/celisa/Heart-Rate-Variability-Repo/main/01_data/7195417.ECG3710114AnesEvents-6%2B10mins_RRI.txt')
```

```{r}
plot(BIS_1)
plot(RRI_1)
plot(BIS_2)
plot(RRI_2)
plot(BIS_3)
plot(RRI_3)
```

```{r}
library(TSA)
acf(RRI_1, lag.max = 50, main = "Sample ACF for Patient 1", cex.main = 0.75, cex.lab = 0.75, cex.axis = 0.5)
acf(RRI_2, lag.max = 50, main = "Sample ACF for Patient 1", cex.main = 0.75, cex.lab = 0.75, cex.axis = 0.5)
acf(RRI_3, lag.max = 50, main = "Sample ACF for Patient 1", cex.main = 0.75, cex.lab = 0.75, cex.axis = 0.5)

```


